oscar_figures

### 2021-03-14 oscar_figures.Rmd
Add barplot of targeted RNA-seq

```{r message=FALSE, warning=FALSE}
read_length_filter <- 29  # length of reads of interest
gencode_v29_info <- read_tsv(paste0(here(), "/data/longest_proteincoding_transcript_hs_details.txt"))
ribo_df <- read_tsv(paste0(here(), "/data/riboseq/sh_tdpb.Aligned.toTranscriptome.out.bam.bed.gz"), 
                    col_names = c("transcript_id", "start0", "end", "strand")) %>%
    inner_join(gencode_v29_info, by = "transcript_id") %>%
    dplyr::filter(end-start0 == read_length_filter) %>%
    mutate(distance_from_start = start0-cds_start) %>%
    group_by(distance_from_start) %>%
    mutate(n_this_dist = n()) %>%
    dplyr::select(distance_from_start, n_this_dist) %>%
    unique()

@@

## Ribosome profiling

@@

>>>>

```{r message=FALSE, warning=FALSE}
read_length_filter <- 29  # length of reads of interest
gencode_v29_info <- read_tsv(paste0(here(), "/data/longest_proteincoding_transcript_hs_details.txt"))
ribo_df <- read_tsv(paste0(here(), "/data/riboseq/sh_tdpb.Aligned.toTranscriptome.out.bam.bed.gz"), 
                    col_names = c("transcript_id", "start0", "end", "strand")) %>%
    inner_join(gencode_v29_info, by = "transcript_id") %>%
    dplyr::filter(end-start0 == read_length_filter, strand == "+") %>%
    mutate(distance_from_start = start0-cds_start) %>%
    group_by(distance_from_start) %>%
    mutate(n_this_dist = n()) %>%
    dplyr::select(distance_from_start, n_this_dist) %>%
    unique()

@@

## Ribosome profiling volcano plot

@@

## Targeted RNA-seq

Read in data from processed bam files

```{r message=FALSE, warning=FALSE}
specific_rt <- read_csv(paste0(here(), "/data/targeted_RNA_seq/specific_RT_primer/for_plot.csv")) %>%
    select(risk, sample_name, n)

random_hexamer <- read_csv(paste0(here(), "/data/targeted_RNA_seq/random_hexamer/values_for_plot.csv")) %>%
    select(-sample_name) %>%
    select(sample_name = actual_sample_name, risk, n)

tg_rnaseq_df <- bind_rows(specific_rt, random_hexamer) %>%
  group_by(sample_name) %>%
  mutate(n_healthy = ifelse(risk == "Non-Risk", n, 0)) %>%
  mutate(combined_healthy = sum(n_healthy)) %>%
  select(-n_healthy) %>%
  mutate(combined = sum(n)) %>%
  group_by(sample_name, risk) %>%
  mutate(combined_n = sum(n)) %>%
  ungroup() %>%
  select(-n) %>%
  unique() %>%
  group_by(sample_name) %>%
  mutate(p_value = pbinom(combined_healthy, sum(combined_n), 0.5)) %>%  # single-tailed bionomial test
  mutate(colour = ifelse(risk == "Non-Risk", "lightblue", "red")) %>%
  ungroup() %>%
  mutate(sample_name_ordered = fct_reorder(sample_name, dplyr::desc(combined_n)))

ggplot(tg_rnaseq_df %>%
         filter(combined_n > 0), aes(x = sample_name_ordered, y = combined_n, fill = risk)) +
  geom_bar(stat="identity", position="dodge") +
  geom_text(aes(x=sample_name, y=-2.5, label=signif(p_value,2)), size = 3.5) +
  xlab("") +
  ylab("Unique cDNAs") +
  ggeasy::easy_add_legend_title("Allele") +
  theme_minimal() +
  ggpubr::theme_pubr() +
  ggeasy::easy_rotate_x_labels()
```

## iCLIP

##
